\section{Related Work}
\label{sec:related}

Our work sits at the intersection of three lines: classical and semiparametric
models for dependent censoring, deep generative survival analysis, and
distribution-matching regularizers built on Nelson--Aalen-style estimators.

\paragraph{Classical and copula-based dependent censoring.}
The non-identifiability of the joint distribution of $(T, C)$ from right-censored
observations has been known since \citet{tsiatis1975nonidentifiability}: without
structural assumptions, the marginal of $T$ is not uniquely recoverable when
$T$ and $C$ are dependent. The dominant statistical response has been to
impose a parametric copula on $(T, C)$ together with parametric marginals and
to prove identifiability under those joint assumptions. \citet{czado2023dependent}
characterize identifiability in this setting through tail-density ratio conditions
on the marginals (their Condition C1) and tail-derivative conditions on the
copula (their Condition C2), and show that Condition C1 is satisfied by the
Weibull, log-normal, log-logistic, and log-Student families. The same authors'
\textsc{depCensoring} R package provides reference implementations of these
estimators. \citet{deresa2021semiparametric} relax the parametric marginal
assumption to a semiparametric normal transformation model, in which $(h(T), h(C))$
follows a bivariate normal distribution with possibly non-diagonal covariance
after a nonparametric monotone transformation $h$, and prove that the model
is identifiable with consistent and asymptotically normal estimators. More
recent extensions move toward covariate-dependent copulas via gradient boosting
\citep{verstraete2025boosting} and quantile regression formulations
\citep{debacker2025quantile}.

Two design choices distinguish this entire line from the deep generative
methods (including ours): (i) the dependence between $T$ and $C$ is encoded
explicitly through a copula or a fixed bivariate latent law, and (ii) the
marginal model class is constrained enough to admit closed-form identifiability
arguments. Our work trades the explicit copula for an implicit
shared-latent encoding via a normalizing flow; we discuss the resulting
identifiability gap and a path to closing it via the C1/C2 framework in
Section~\ref{sec:identifiability}.

\paragraph{Deep generative survival analysis.}
Conditional generative models for survival data have proliferated in the
last five years. \citet{nagpal2021dsm} (Deep Survival Machines) parameterize
the conditional density of $T \mid Z$ as a learnable mixture of LogNormal or
Weibull components, trained by censored maximum likelihood. \citet{ausset2021conditional}
were among the first to apply conditional normalizing flows to survival data,
working in the uninformative-censoring regime with a $T$-only model.
\citet{lee2018deephit} (DeepHit) and \citet{tang2022soden} (SODEN) use
discrete-time hazards and ODE-based hazards, respectively. \citet{norcliffe2023survivalgan}
explore GAN-style generative survival modeling. None of these works explicitly
handle informative censoring with a joint generative model.

The most closely related deep methods for \emph{dependent} censoring are
\citet{ding2023copula} and the subsequent \citet{zhang2024deepcopula}
(\textsc{DCSurvival}). Both use deep neural networks to parameterize the
marginal distributions of $T$ and $C$ but retain an explicit Archimedean
copula head to model the dependence. \textsc{DCSurvival} establishes
identifiability of its model by directly invoking the Czado--Van Keilegom
Theorem~3 \citep{czado2023dependent}, leveraging the fact that the deep
marginals (Weibull / log-normal heads) satisfy Condition C1. \citet{lillelund2024mensa}
(\textsc{MENSA}) extends the deep multi-event setting to informative censoring
through joint mixture-marginal parametrizations, but does not address
identifiability. Compared to all three of these, our method differs in two
ways: we replace the explicit copula with a shared-latent variable, and we
allow the marginal flow to be strictly more expressive than any
log-location-scale family.

\paragraph{Wasserstein- and Nelson--Aalen-based regularization for survival.}
\citet{sylvain2021wasserstein} introduced a Wasserstein metric between
Kaplan--Meier-imputed CDFs as a discriminative loss for survival prediction.
\citet{zhou2024wkm} subsequently developed Wasserstein--Kaplan--Meier
survival regression, in which Kaplan--Meier curves are treated as
Wasserstein-space objects and regressed against covariates through a
Fr\'echet regression framework, providing the first principled
distribution-on-distribution interpretation of the Wasserstein--KM objective.
Our Soft--Nelson--Aalen Wasserstein regularizer is generative rather than
discriminative or regression-based: it matches the model-implied population
survival curve to the empirical one through differentiable sampling, allowing
the regularizer to backpropagate end-to-end into both the marginal flows and
(in the informative case) the shared-latent encoding. The use of differentiable sampling through
implicit reparameterization, in the sense of \citet{figurnov2018implicit},
is what makes the Soft--NA + Wasserstein objective trainable in the flow
setting; without it, the bisection-based inverse of the flow blocks gradient
flow into the flow parameters.

\paragraph{Position of this work.}
We propose a conditional normalizing flow for joint $(T, C)$ modeling
under both uninformative and informative right censoring, with closed-form
censored MLE in the forward direction and exact-gradient differentiable
sampling in the inverse direction via implicit reparameterization.
While prior work has applied conditional flows to
$T$-only survival modeling \citep{ausset2021conditional}, we extend
the approach to the joint $(T, C)$ setting with a shared-latent
informative censoring mechanism. Compared to copula-based statistical methods
\citep{czado2023dependent,deresa2021semiparametric,zhang2024deepcopula}, our
method does not specify a copula family and admits a strictly more flexible
marginal class. Compared to deep generative survival baselines that target
only the uninformative regime \citep{nagpal2021dsm,ausset2021conditional,
norcliffe2023survivalgan}, we handle the shared-frailty informative censoring
case through Monte Carlo marginalization of the latent variable. We discuss
the price of dropping the explicit copula --- the loss of a closed-form
identifiability proof --- in Section~\ref{sec:identifiability}, where we
sketch an extension of the Czado--Van Keilegom C1 condition to our flow class.
