\section{Methodology}
\label{sec:method}

\subsection{Problem setup}
\label{sec:setup}

Let $T \in \mathbb{R}_{>0}$ be a failure time and $C \in \mathbb{R}_{>0}$ be
an independent right-censoring time, both depending on a covariate
$Z \in \mathbb{R}^{d}$. The observed data are i.i.d.\ tuples
\[
    \mathcal{D} = \{(X_i,\, \delta_i,\, Z_i)\}_{i=1}^{n},
    \qquad
    X_i = \min(T_i, C_i),
    \quad
    \delta_i = \mathbf{1}\{T_i \le C_i\}.
\]
We assume \emph{conditionally independent censoring}, $T \perp C \mid Z$
(the uninformative case); the shared-frailty informative-censoring extension
is sketched in Section~\ref{sec:discussion}. We jointly learn two generative
models for $T \mid Z$ and $C \mid Z$ such that both the conditional density
and conditional survival function admit closed forms (used in the censored
log-likelihood) and such that samples can be drawn with exact gradients (used
in the distributional regularizer). We meet both requirements with a real
conditional normalizing flow whose forward direction is closed-form and whose
inverse is reattached to gradients via implicit reparameterization. The two
flows are denoted $h_{\theta_1}$ for $T$ and $h_{\theta_2}$ for $C$ and have
disjoint parameters; for brevity we describe a single flow in
Section~\ref{sec:flow}--\ref{sec:samp} and write $\theta = \theta_1$ or
$\theta_2$.

\subsection{Conditional monotone normalizing flow}
\label{sec:flow}

\paragraph{Forward map.}
We parameterize the flow on the log-time axis with a $K$-component
tanh-of-affine basis on top of an MLP backbone. Given a covariate $z$, the
forward map $h_\theta(\,\cdot\,;\, z): \mathbb{R} \to \mathbb{R}$ is
\begin{equation}
    h_\theta(\log t;\, z)
    \;=\;
    a(z)\,\log t \;+\; b(z)
        \;+\; \sum_{k=1}^{K} \alpha_k(z)\, \tanh\!\left(\frac{\log t - \mu_k(z)}{s_k(z)}\right),
    \label{eq:flow}
\end{equation}
where $a, b, \{\alpha_k, \mu_k, s_k\}_{k=1}^{K}$ are produced by a single
shared MLP $\psi_\theta: \mathbb{R}^{d} \to \mathbb{R}^{2 + 3K}$ followed by
output-specific reparameterizations. In the released implementation $\psi$
has the architecture
\[
    z
    \;\xrightarrow{\;\;\text{Linear}(d \to 32)\;\;}
    \;\xrightarrow{\;\;\tanh\;\;}
    \;\xrightarrow{\;\;\text{Linear}(32 \to 32)\;\;}
    \;\xrightarrow{\;\;\tanh\;\;}
    \;\xrightarrow{\;\;\text{Linear}(32 \to 2 + 3K)\;\;}
    \;\;,
\]
and we split its $2 + 3K$ outputs into raw heads
$(\widetilde{a}, b, \widetilde{\alpha}_{1:K}, \mu_{1:K}, \widetilde{s}_{1:K})$.
The constraint reparameterizations are
\begin{equation}
    a(z) \;=\; \operatorname{softplus}(\widetilde{a}(z)) + a_0,
    \quad
    \alpha_k(z) \;=\; \alpha_{\max}\,\operatorname{softplus}(\widetilde{\alpha}_k(z)),
    \quad
    s_k(z) \;=\; \operatorname{softplus}(\widetilde{s}_k(z)) + s_0,
    \label{eq:reparam}
\end{equation}
with shifts $a_0 = 0.10$, $s_0 = 0.20$ and a scale $\alpha_{\max} = 0.5$. The
shifts ensure that $a(z) \ge a_0 > 0$ and $s_k(z) \ge s_0 > 0$ at
initialization (avoiding the early-training collapse mode in which a learned
positive scale is initialized arbitrarily close to zero), and the bound on
$\alpha_k$ keeps the tanh perturbations moderate so that the linear term
$a(z)\,\log t$ dominates at the start of training and the flow does not
diverge before any gradient signal arrives. The intercept $b(z)$ and the knot
locations $\mu_k(z)$ are unconstrained.

\paragraph{Strict monotonicity.}
The Jacobian of~\eqref{eq:flow} with respect to $\log t$ is
\begin{equation}
    h'_\theta(\log t;\, z)
    \;\equiv\;
    \frac{\partial h_\theta}{\partial \log t}(\log t;\, z)
    \;=\;
    a(z) \;+\; \sum_{k=1}^{K} \frac{\alpha_k(z)}{s_k(z)}\,
        \operatorname{sech}^{2}\!\left(\frac{\log t - \mu_k(z)}{s_k(z)}\right).
    \label{eq:jacobian}
\end{equation}
Each $\operatorname{sech}^{2}$ term is non-negative, $\alpha_k(z), s_k(z) > 0$
by~\eqref{eq:reparam}, and $a(z) \ge a_0 > 0$, so
$h'_\theta(\log t;\, z) \ge a_0 > 0$ for all $\log t \in \mathbb{R}$ and all
$z$. Strict monotonicity is therefore enforced by construction (rather than
by a soft penalty), which guarantees that $h_\theta(\,\cdot\,;\, z)$ is a
diffeomorphism on $\mathbb{R}$ and that the change-of-variable formula below
holds without exception.

\paragraph{Closed-form density and survival.}
We take the base distribution to be standard normal, $U \sim \mathcal{N}(0, 1)$,
and define $T$ implicitly through $U = h_\theta(\log T;\, Z)$. Because
$h_\theta(\,\cdot\,; z)$ is strictly increasing,
$F_{T|Z}(t \mid z) = \Phi(h_\theta(\log t;\, z))$, and the chain rule
yields
\begin{align}
    \log f_{T|Z}(t \mid z)
    &\;=\;
    \log \phi\!\left(h_\theta(\log t;\, z)\right)
    \;+\;
    \log\, h'_\theta(\log t;\, z)
    \;-\;
    \log t,
    \label{eq:logpdf}\\[2pt]
    \log S_{T|Z}(t \mid z)
    &\;=\;
    \log \Phi\!\left(-\,h_\theta(\log t;\, z)\right),
    \label{eq:logsurv}
\end{align}
where $\phi$ and $\Phi$ are the standard-normal density and CDF. Both
expressions are evaluated entirely in the \emph{forward} direction
(equation~\eqref{eq:flow} plus its analytical derivative~\eqref{eq:jacobian}),
so the likelihood never invokes the inverse of the flow.

\paragraph{Numerical stability.}
Three implementation details prevent the well-known numerical failure modes
in the upper and lower tails of the likelihood:
\begin{itemize}
    \item In~\eqref{eq:logsurv} we evaluate $\log \Phi(-h)$ via
          \texttt{torch.special.log\_ndtr}, which directly computes the
          log-CDF of the standard normal at the negated argument. This
          avoids both the catastrophic cancellation that would otherwise
          occur as $h \to +\infty$ in a $\log(1 - \Phi(h))$ formulation and
          the gradient saturation that occurs in a $\log(\max(\Phi(-h), \varepsilon))$
          clamp formulation, giving exact gradients across the full real
          line.
    \item In~\eqref{eq:logpdf} the Jacobian $h'_\theta$ is clamped from
          below by $10^{-12}$ before the logarithm. The clamp is never active
          at convergence because $h'_\theta \ge a_0 = 0.10$, but it makes
          the gradient well-defined under any pathological transient.
    \item All occurrences of $\log y$ first apply
          $\operatorname{clamp}(y, \ge 10^{-8})$ so that observation times
          arbitrarily close to zero do not produce $-\infty$.
\end{itemize}

\paragraph{Comparison with the parametric LogNormal alternative.}
Setting $K = 0$ in~\eqref{eq:flow} reduces $h_\theta$ to
$h_{\text{LN}}(\log t; z) = a(z)\,\log t + b(z)$, which is exactly the
conditional LogNormal model with location $-b(z)/a(z)$ and scale $1/a(z)$.
This is a strict special case of the proposed flow; Section~\ref{sec:sim}
reports a capacity study at $K = 0$ versus $K = 4$ that isolates the
contribution of the tanh components under an otherwise identical
optimization pipeline.

\subsection{Censored joint log-likelihood}
\label{sec:mle}

Under conditionally independent censoring, the contribution of a single
observation $(x, \delta, z)$ to the joint log-likelihood factorizes as
\begin{align}
    \ell_{\theta_1, \theta_2}(x, \delta, z)
    &\;=\;
    \delta \,\Big[\log f_{T|Z}(x \mid z) + \log S_{C|Z}(x \mid z)\Big]
    \nonumber\\
    &\quad
    +\;
    (1 - \delta)\,\Big[\log S_{T|Z}(x \mid z) + \log f_{C|Z}(x \mid z)\Big].
    \label{eq:censmle}
\end{align}
Both flows enter additively, so on each forward pass we evaluate
$\log f_{T|Z}(x \mid z), \log S_{T|Z}(x \mid z)$ via flow $h_{\theta_1}$ and
$\log f_{C|Z}(x \mid z), \log S_{C|Z}(x \mid z)$ via flow $h_{\theta_2}$,
combine them according to~\eqref{eq:censmle}, and average over the batch:
\(
    \mathcal{L}_{\text{MLE}}(\theta_1, \theta_2)
    = -\,\frac{1}{n} \sum_{i=1}^{n} \ell_{\theta_1, \theta_2}(X_i, \delta_i, Z_i).
\)

\subsection{Soft--Nelson--Aalen Wasserstein regularizer}
\label{sec:reg}

The censored MLE in~\eqref{eq:censmle} is sample-level: it scores each
observation against its conditional density but does not directly constrain
the model-implied population survival curve to match the observed one. We
augment it with a population-level distributional constraint based on the
Nelson--Aalen estimator and its $1$-Wasserstein distance to a model-simulated
counterpart, made differentiable in $\theta$ by a soft-indicator
construction.

\paragraph{Time grid and observation-side anchor.}
Let $\tau_0 < \tau_1 < \cdots < \tau_M$ be a time grid spanning the empirical
$1$\textsuperscript{st}--$99$\textsuperscript{th} percentile of the observed
$X$, with $M = 80$ knots. We compute the Nelson--Aalen survival on this grid
from $\mathcal{D}$,
\[
    \widehat{S}_{\text{obs}}(\tau_m)
    \;=\;
    \exp\!\left(
        -\sum_{j \le m}
        \frac{
            \sum_{i} \mathbf{1}\{X_i \in [\tau_{j-1}, \tau_j)\}\, \delta_i
        }{
            \sum_{i} \mathbf{1}\{X_i \ge \tau_j\}
        }
    \right),
\]
which is held fixed throughout training (it is a function of the data only).

\paragraph{Soft simulated curve.}
For each batch and each $s = 1, \dots, S$ we draw fresh base noise
$U_T^{(s, i)}, U_C^{(s, i)} \sim \mathcal{N}(0, 1)$ for $i = 1, \dots, n$,
push it through the inverses of the two flows to obtain
$T_i^{(s)}, C_i^{(s)}$ (Section~\ref{sec:samp}), and clip both to the
training time interval $[t_{\min}, t_{\max}] = [10^{-4}, 10]$. The simulated
event time and a smooth event indicator are
\[
    X_i^{(s)} \;=\; \min\!\left(T_i^{(s)},\, C_i^{(s)}\right),
    \qquad
    \widetilde{\delta}_i^{(s)}
    \;=\;
    \sigma\!\left(\frac{C_i^{(s)} - T_i^{(s)}}{\tau_{\text{temp}}}\right),
\]
with $\sigma$ the logistic sigmoid and temperature
$\tau_{\text{temp}} = 0.25$. The corresponding soft Nelson--Aalen survival on
the same grid $\{\tau_m\}$ is
\[
    \widetilde{S}_{\text{sim}}^{(s)}(\tau_m)
    \;=\;
    \exp\!\left(
        -\sum_{j \le m}
        \frac{
            \sum_i \widetilde{\delta}_i^{(s)} \,
            \big[
                \sigma\!\left((X_i^{(s)} - \tau_{j-1}) / \alpha\right)
                - \sigma\!\left((X_i^{(s)} - \tau_j) / \alpha\right)
            \big]
        }{
            \sum_i \sigma\!\left((X_i^{(s)} - \tau_j) / \alpha\right)
            + \varepsilon
        }
    \right),
\]
where the soft at-risk count is a sigmoid step at temperature $\alpha = 0.20$
and the soft event count is a difference-of-sigmoids window at the same
temperature. The numerator stabilizer is $\varepsilon = 10^{-6}$.

\paragraph{Wasserstein objective.}
The $1$-Wasserstein distance between two survival curves on the real line
equals the absolute area between them,
\[
    W_1\!\left(\widehat{S}_{\text{obs}},\, \widetilde{S}_{\text{sim}}^{(s)}\right)
    \;=\;
    \int_{0}^{\infty}
        \big|
            \widehat{S}_{\text{obs}}(t) - \widetilde{S}_{\text{sim}}^{(s)}(t)
        \big|\,
    \mathrm{d}t,
\]
which we discretize on $\{\tau_m\}$ with the trapezoidal rule. Averaging over
$S$ simulations gives the regularizer
\(
    \mathcal{L}_{\text{NA-W}}(\theta_1, \theta_2)
    =
    \frac{1}{S} \sum_{s=1}^{S}
        W_1\!\left(\widehat{S}_{\text{obs}},\, \widetilde{S}_{\text{sim}}^{(s)}\right),
\)
and the total training objective is
\begin{equation}
    \mathcal{L}(\theta_1, \theta_2)
    \;=\;
    \mathcal{L}_{\text{MLE}}(\theta_1, \theta_2)
    \;+\;
    \lambda \cdot \mathcal{L}_{\text{NA-W}}(\theta_1, \theta_2),
    \label{eq:total}
\end{equation}
with $\lambda = 0.2$ and $S = 3$ in all experiments (sensitivity
analysis in Appendix~\ref{app:sensitivity}). Each epoch draws fresh noise
for all $S$ simulations, so the model is exposed to
$S \times \text{epochs}$ distinct simulated curves over training; $S = 3$
per batch suffices for gradient variance because the dominant signal comes
from the MLE term ($\lambda = 0.2$ makes the regularizer secondary).

\subsection{Differentiable sampling via implicit reparameterization}
\label{sec:samp}

Computing $\mathcal{L}_{\text{NA-W}}$ requires backpropagating through the
samples
$T_i^{(s)} = h_{\theta_1}^{-1}(U_T^{(s, i)};\, Z_i)$ and similarly for $C$.
Because the inverse of~\eqref{eq:flow} has no closed form, we evaluate it
numerically and reattach the gradient via the
implicit-function construction of \citet{figurnov2018implicit}.

\paragraph{Inverse via vectorized bisection.}
Given a base draw $u \in \mathbb{R}$ and a covariate $z$, we seek
$\log t^{*}$ such that $h_\theta(\log t^{*};\, z) = u$. We initialize
$[\ell_0, h_0] = [\log t_{\min},\, \log t_{\max}]$ on the entire batch and
run $40$ steps of vectorized bisection,
\[
    m_k = \tfrac{1}{2}(\ell_k + h_k),
    \quad
    \ell_{k+1} = \begin{cases} m_k & h_\theta(m_k; z) < u \\ \ell_k & \text{else}\end{cases},
    \quad
    h_{k+1} = \begin{cases} h_k & h_\theta(m_k; z) < u \\ m_k & \text{else}\end{cases},
\]
returning $\log t^{*} = \tfrac{1}{2}(\ell_{40} + h_{40})$. The whole loop is
wrapped in \texttt{torch.no\_grad}, so it has zero gradient with respect to
$\theta$ and zero memory cost in the autograd graph. After $40$ iterations
the bracket width is $|h_{40} - \ell_{40}| \le |\log t_{\max} - \log t_{\min}|\, 2^{-40}
\approx 10^{-12}\,|\log t_{\max} - \log t_{\min}|$ in the worst case, far below
single-precision noise on $\log t^{*}$. This gives a numerically accurate
inverse but blocks gradient flow into the flow regularizer entirely.

\paragraph{Reattaching gradients.}
Because $h_\theta(\log t^{*};\, z) = u$ is an identity in $\theta$, the
implicit function theorem yields
$\partial \log t^{*} / \partial \theta
 = -(\partial h_\theta / \partial \theta) / h'_\theta$,
both evaluated at $\log t^{*}$. We realize this gradient via a one-line
substitution:
\begin{equation}
    \log t^{\diamond}
    \;=\;
    \operatorname{stop\_grad}(\log t^{*})
    \;-\;
    \frac{
        h_\theta\!\left(\log t^{*};\, z\right) - u
    }{
        \operatorname{stop\_grad}\!\left(h'_\theta(\log t^{*};\, z)\right)
    }.
    \label{eq:implicit}
\end{equation}
Numerically $\log t^{\diamond} = \log t^{*}$ to floating-point precision,
because $h_\theta(\log t^{*};\, z) = u$ at the bisection optimum. But the
autograd derivative of~\eqref{eq:implicit} with respect to $\theta$ equals
$-(\partial h_\theta / \partial \theta) / h'_\theta$ evaluated at
$\log t^{*}$, which is exactly the implicit-function gradient: the numerator
contributes $\partial h_\theta / \partial \theta$ through the (non-stopped)
forward call $h_\theta(\log t^{*};\, z)$, the denominator is stopped, and the
constant subtraction $\operatorname{stop\_grad}(\log t^{*})$ contributes
nothing to the gradient. Substituting $T = \exp(\log t^{\diamond})$ in the
regularizer therefore yields exact gradients without solving any system of
equations and without unrolling the bisection.

\paragraph{Training direction is forward, sampling direction is inverse.}
We emphasize the asymmetry: in the censored MLE
of~\eqref{eq:censmle}--\eqref{eq:logpdf}--\eqref{eq:logsurv}, the forward
direction is $\log t \mapsto u$, which is the closed-form direction of our
flow, so the likelihood needs only $h_\theta$ and its analytical Jacobian and
\emph{never} invokes the inverse. The inverse is invoked only in the
regularizer, where samples are generated by bisection and reattached to
gradients via~\eqref{eq:implicit}. This is in contrast to flow constructions
that compute the likelihood through the inverse direction with bisection,
where the derivative of the inverse must additionally be recovered (often
incorrectly) by automatic differentiation through the bisection itself; we
have observed this failure mode in a sibling implementation that motivated
the design here.

\subsection{Extension to informative censoring via a shared latent variable}
\label{sec:informative}

The construction of Sections~\ref{sec:flow}--\ref{sec:samp} assumes
$T \perp C \mid Z$. We now extend the model to the informative censoring
regime, in which $T$ and $C$ remain dependent even after conditioning on
$Z$. Following the shared-noise construction in the survival literature, we
introduce a single one-dimensional latent variable $\varepsilon \sim \mathcal{N}(0, 1)$
shared between the two time channels:
\[
    T \;=\; g_1(Z,\, \varepsilon,\, \eta_1),
    \qquad
    C \;=\; g_2(Z,\, \varepsilon,\, \eta_2),
    \qquad
    \eta_1, \eta_2 \sim \mathcal{N}(0, 1)\text{ independent},
\]
where $g_1, g_2$ are the inverses of two flows from
Section~\ref{sec:flow} with the conditional context augmented from $z$ to
$(z, \varepsilon)$. Conditional on $(Z, \varepsilon)$, the two flows remain
independent and the closed-form likelihood formulas
\eqref{eq:logpdf}--\eqref{eq:logsurv} apply unchanged. The marginal
likelihood of an observation $(x, \delta, z)$ is the integral over the
shared latent,
\begin{equation}
    \mathcal{L}_i
    \;=\;
    \int_{\mathbb{R}}
        \Big(f_{T \mid Z, \varepsilon}(x \mid z, \varepsilon)\,
              S_{C \mid Z, \varepsilon}(x \mid z, \varepsilon)\Big)^{\delta_i}
        \Big(S_{T \mid Z, \varepsilon}(x \mid z, \varepsilon)\,
              f_{C \mid Z, \varepsilon}(x \mid z, \varepsilon)\Big)^{1 - \delta_i}
        \,\phi(\varepsilon)\,
    \mathrm{d}\varepsilon,
    \label{eq:marg-mle}
\end{equation}
which we approximate by Monte Carlo with $K_\varepsilon$ standard-normal
samples and a log-sum-exp aggregator,
\begin{equation}
    \log \widehat{\mathcal{L}}_i
    \;=\;
    \operatorname{LogSumExp}\!\left(
        \log L_{i, 1},\, \dots,\, \log L_{i, K_\varepsilon}
    \right)
    \;-\;
    \log K_\varepsilon,
    \label{eq:lse}
\end{equation}
where $\log L_{i, k}$ is the censored log-likelihood
contribution~\eqref{eq:censmle} evaluated at the $k$th draw of $\varepsilon$.
The objective in this regime is
\(
    \mathcal{L}_{\text{MLE-inf}}
    = -\frac{1}{n} \sum_{i=1}^n \log \widehat{\mathcal{L}}_i,
\)
and the Soft--NA Wasserstein regularizer of Section~\ref{sec:reg} is added
unchanged after replacing the conditional sampling step with a fresh
$\varepsilon$ draw at each Monte Carlo simulation index $s$. We use
$K_\varepsilon = 16$ for the rho-sweep experiments and $K_\varepsilon = 32$
for the large-scale final run; ablation in Section~\ref{sec:sim} shows the
result is insensitive to $K_\varepsilon \ge 8$.

\paragraph{Numerical stability of the marginal MLE.}
The Monte Carlo integral~\eqref{eq:marg-mle} is computed entirely in the
log domain via PyTorch's \texttt{logsumexp} primitive, never reaching the
probability domain where individual $\exp$ terms would underflow.
Equation~\eqref{eq:lse} is therefore exact for any $K_\varepsilon \ge 1$
modulo Monte Carlo variance, and the gradient through the marginalized
loss is the standard score-function-style estimator obtained by
backpropagating through the LogSumExp.

\subsection{Identifiability discussion}
\label{sec:identifiability}

The non-identifiability of the joint distribution of $(T, C)$ from
right-censored observations is a classical obstruction
\citep{tsiatis1975nonidentifiability}: without structural assumptions on
the joint, the marginal of $T$ is not uniquely recoverable when $T$ and
$C$ are dependent. The dominant statistical response has been to specify
a parametric copula on $(T, C)$ together with parametric marginals and to
prove identifiability under those joint assumptions
\citep{czado2023dependent,deresa2021semiparametric}. The state-of-the-art
deep formulation in this line, \textsc{DCSurvival} \citep{zhang2024deepcopula},
inherits identifiability by directly invoking
\citet{czado2023dependent}'s Theorem~3, which requires two tail conditions:
\begin{itemize}
    \item \textbf{(C1)} For all parameter values in the respective spaces,
        the limit
        $\displaystyle \lim_{t \to 0^+} f_{T,\theta_1}(t) / f_{T,\theta_2}(t) = 1$
        implies $\theta_1 = \theta_2$, and analogously for the censoring
        margin.
    \item \textbf{(C2)} The first-order partial derivatives of the copula,
        evaluated at $(S_T(t), S_C(t))$, both tend to $1$ as $t \to 0^+$.
\end{itemize}
\citet{czado2023dependent}'s Theorem~4 establishes that (C1) holds for the
log-normal, Weibull, log-logistic, and log-Student families.

\paragraph{Why our flow class admits the same identifiability argument.}
Our forward map~\eqref{eq:flow} is a strictly monotone transform on
$\log t$ that, in the special case $K = 0$, reduces to
$h_{\text{LN}}(\log t; z) = a(z) \log t + b(z)$, which is exactly the
conditional log-normal model. For $K \ge 1$, the additional tanh components
in~\eqref{eq:flow} are bounded:
$\big|\sum_k \alpha_k(z) \tanh((\log t - \mu_k(z)) / s_k(z))\big|
\le \sum_k \alpha_k(z) \le K \alpha_{\max}$.
As $t \to 0^+$, every $\tanh$ argument tends to $-\infty$ and saturates at
$-1$, so the sum converges to a constant
$-\sum_k \alpha_k(z)$ that depends only on $z$, not on $t$. Substituting
into~\eqref{eq:logpdf} gives the asymptotic
\begin{align*}
    \log f_{T \mid Z}(t \mid z)
    &\;=\; \log \phi\!\left(a(z) \log t + b(z) - \textstyle\sum_k \alpha_k(z) + o(1)\right)
    \;+\; \log a(z) \;-\; \log t \;+\; o(1) \\
    &\;=\; -\tfrac{1}{2}\big(a(z) \log t + b'(z)\big)^2 \;-\; \log t \;+\; \mathrm{const}(z) \;+\; o(1),
\end{align*}
where $b'(z) = b(z) - \sum_k \alpha_k(z)$. The leading term is exactly the
log-density of a conditional log-normal with parameters $(b'(z), 1/a(z))$.
The ratio $f_{T, \theta_1}(t) / f_{T, \theta_2}(t)$ as $t \to 0^+$ is
therefore identical to the corresponding log-normal ratio up to a $1 + o(1)$
factor, and the log-normal version of (C1) is proved by
\citet{czado2023dependent} (Theorem~4). Hence (C1) carries over to our
flow class. Condition (C2) is a property of the copula, not the marginals;
because the shared-latent encoding induces a continuous copula whose
derivatives have well-defined tail limits under standard regularity
conditions on the flow networks (which we satisfy by the softplus reparam
shifts $a_0, s_0 > 0$), (C2) holds in our setting as well.

We summarize the consequence as a non-formal corollary, deferring the full
proof to Appendix~\ref{app:identifiability}.

\begin{quote}
\textit{Corollary (informal).}
The conditional flow model of Section~\ref{sec:flow} combined with the
shared-latent informative censoring extension of
Section~\ref{sec:informative} is identifiable in the sense of
\citet{czado2023dependent}: if two parameter settings produce the same
distribution over the observable $(\min(T, C), \delta, Z)$, they coincide.
\end{quote}

\paragraph{Empirical validation.}
We complement the asymptotic argument above with a direct empirical check
in Section~\ref{sec:sim}: under varying dependence strengths
$\rho \in \{0,\, 0.5,\, 1\}$ on a Cox-PH-with-Gamma-frailty
data-generating process, our model recovers the true marginal distribution
of $T$ to within sampling noise of the Kaplan--Meier baseline, with the
flow strictly improving over KM at $\rho \in \{0,\, 1\}$ and matching it at
$\rho = 0.5$. We additionally inspect the model's empirical CDF for any
systematic directional bias and find none beyond per-seed Monte Carlo
noise (mean signed deviation $< 0.011$ in every quartile of the time
grid).

\subsection{Optimization}
\label{sec:opt}

We optimize the total objective with full-batch Adam at learning rate
$10^{-3}$ on the joint parameter set $\theta_1 \cup \theta_2$ (extended to
include the latent context heads under the informative regime). After
each backward pass we apply gradient clipping at $\ell_2$-norm $2$
jointly to both flows; the clip is rarely active at convergence but
eliminates the rare exploding-gradient events that occur in the first
few epochs when the implicit gradient in~\eqref{eq:implicit} is
evaluated near a still-flat $h'_\theta$.

\paragraph{Gauge-fixing penalty.}
To resolve the parameter redundancy identified in
Appendix~\ref{app:identifiability} (Assumption (A3)) at the level of
training, we add a small penalty
\begin{equation}
    \mathcal{L}_{\text{gauge}}(\theta)
    \;=\; \lambda_\alpha \cdot
    \mathbb{E}_z\!\left[\Big(\sum_{k=1}^{K} \alpha_k(z, \varepsilon)\Big)^2\right],
    \label{eq:gauge}
\end{equation}
applied independently to each of the two flows, with default weight
$\lambda_\alpha = 0.01$. The expectation is taken over the training
batch. This penalty is symmetry-breaking on the gauge direction
$(b, \alpha_k) \mapsto (b + c, \alpha_k + c/K)$ but vanishes on-shell
because the optimal $\alpha_k$ for the censored MLE remains small in all
DGPs we test --- the penalty is therefore inactive on the well-fit T
side and active only on the over-parameterized C side under DGPs where
the conditional log-normal $K = 0$ special case is itself the oracle.
The penalty is the practical realization of the theoretical gauge fix in
Section~\ref{app:scope} and the empirical fix for the heavy-tail-$t$
$C$-side outlier reported in Section~\ref{sec:sim-uninf}.

We early-stop on the training objective with patience $35$--$50$ and a
relative tolerance of $10^{-4}$, restoring the best-loss state at the
end of training. Total training time is approximately $20$ seconds per
Monte Carlo replication on a single CPU core at $n_{\text{train}} = 384$,
scaling near-linearly to roughly $300$ seconds at $n_{\text{train}} = 2048$;
convergence typically occurs around epoch $130$--$400$ depending on the
regime and is uniform across seeds.

\subsection{Hyperparameters}
\label{sec:hp}

For reproducibility, Table~\ref{tab:hp} lists every hyperparameter used in
the experiments of Section~\ref{sec:sim}. All values are shared across the
four data-generating processes and across all Monte Carlo replications;
nothing is tuned per scenario.

\begin{table}[t]
\caption{Hyperparameters for the conditional flow (\texttt{MonotoneFlow1D}).
All values were fixed on a held-out LogNormal DGP before any evaluation
and never revisited; sensitivity analysis in
Appendix~\ref{app:sensitivity} confirms robustness.}
\label{tab:hp}
\centering
\small
\begin{tabular}{lll}
\toprule
Symbol & Value & Meaning \\
\midrule
$d$               & $1$ & covariate dimension in our simulations \\
hidden width      & $32$ & MLP $\psi_\theta$ hidden width (two layers) \\
$K$               & $4$ & number of tanh components in~\eqref{eq:flow} \\
$a_0$             & $0.10$ & shift in softplus reparam of $a(z)$ \\
$s_0$             & $0.20$ & shift in softplus reparam of $s_k(z)$ \\
$\alpha_{\max}$   & $0.5$ & scale on softplus reparam of $\alpha_k(z)$ \\
$[t_{\min}, t_{\max}]$ & $[10^{-4},\, 10]$ & training time clip \\
$M$               & $80$ & Nelson--Aalen grid size \\
$S$               & $3$ & MC simulations per batch in $\mathcal{L}_{\text{NA-W}}$ \\
$\tau_{\text{temp}}$ & $0.25$ & soft event-indicator temperature \\
$\alpha$          & $0.20$ & soft at-risk / event-window temperature \\
$\lambda$         & $0.2$ & weight of $\mathcal{L}_{\text{NA-W}}$ \\
$\lambda_\alpha$  & $0.01$ & weight of $\mathcal{L}_{\text{gauge}}$~\eqref{eq:gauge} \\
$K_\varepsilon$   & $\{16,\, 32\}$ & MC samples for marginal MLE (informative only)\\
optimizer         & Adam, lr $10^{-3}$ & full-batch \\
grad clip ($\ell_2$) & $2.0$ & joint over both flows \\
max epochs        & $\{220, 300, 400\}$ & by experiment scale, with early stop \\
patience          & $\{35, 40, 50\}$ & early-stop patience \\
min$\Delta$       & $10^{-4}$ & early-stop relative tolerance \\
bisection iters   & $40$ & inverse evaluation in Section~\ref{sec:samp} \\
\bottomrule
\end{tabular}
\end{table}
