\section{Simulation Studies}
\label{sec:sim}

We organize the simulation study in three parts:
Section~\ref{sec:sim-uninf} validates the conditional flow under
uninformative censoring on five data-generating processes (DGPs),
Section~\ref{sec:sim-inf} validates the shared-latent extension under
informative censoring on two distinct frailty DGPs across three
dependence strengths, and Section~\ref{sec:sim-discussion} discusses
the role of the Wasserstein regularizer and standard survival metrics.
Across all parts, we report mean $\pm$ standard deviation across
$30$--$50$ Monte Carlo replications.

\subsection{Setup common to both regimes}
\label{sec:sim-setup}

Throughout, the covariate $Z$ is one-dimensional standard normal. Times
are clipped to $[10^{-4},\, 10]$ for both true and simulated samples.
Training uses full-batch Adam with the hyperparameters in
Table~\ref{tab:hp}, scaled to two operating points:
\begin{itemize}
    \item \textbf{Main scale.} $n_{\text{train}} = 1024$,
          $n_{\text{eval}} = 512$, $30$ Monte Carlo replications,
          maximum $300$ epochs.
    \item \textbf{Large scale (\emph{bigN}).} $n_{\text{train}} = 2048$,
          $n_{\text{eval}} = 1024$, $30$--$50$ Monte Carlo replications
          (50 for the base scenario, $30$ for the rest), maximum $400$
          epochs.
\end{itemize}
The model marginal $T$ distribution at evaluation time is estimated by
drawing $S_{\text{eval}} = 20$ shared-latent samples per held-out
covariate, giving $S_{\text{eval}} \cdot n_{\text{eval}}$ effective model
draws. We compare these against the same number of true samples from the
DGP. The Wasserstein-1 metric between the two empirical CDFs is computed
in the absolute-area form on a $300$-point time grid spanning the pooled
$1$\textsuperscript{st}--$99.5$\textsuperscript{th} percentile.

\paragraph{Baselines.}
We compare against four classical baselines and three recent deep methods:
\begin{itemize}
    \item \textbf{Kaplan--Meier (KM).} Nonparametric, no covariate.
    \item \textbf{Cox PH.} Semiparametric proportional hazards with linear
          $Z$ effect, fit by partial likelihood, with a Breslow baseline
          cumulative hazard for the marginal CDF.
    \item \textbf{AFT-LogNormal} and \textbf{AFT-Weibull.} Parametric AFT
          regressions with linear $Z$ effect, fit by maximum likelihood.
    \item \textbf{DSM} \citep{nagpal2021dsm}. Deep Survival Machines: a
          mixture of $K{=}4$ conditional log-normals, trained by censored
          MLE. Models $T$ only; assumes independent censoring.
    \item \textbf{WKM} \citep{zhou2024wkm}. Wasserstein--Kaplan--Meier
          regression: kernel-weighted KM curves over covariate bins.
          Models $T$ only; assumes independent censoring.
    \item \textbf{DCSurvival} \citep{zhang2024deepcopula}. Deep LogNormal
          marginals coupled by a Frank survival copula with a learnable
          dependence parameter $\alpha$, trained by copula-augmented
          censored MLE. The only competing method that explicitly models
          $T$-$C$ dependence.
    \item \textbf{T-only flow} \citep{ausset2021conditional}. A
          conditional normalizing flow trained with standard censored MLE
          for $T$ only (no $C$ model, no Wasserstein regularizer). Uses
          the same $K{=}4$ MonotoneFlow1D architecture as our method,
          isolating the contribution of joint $(T, C)$ modeling and the
          regularizer.
\end{itemize}
For the uninformative experiments, we additionally report a
\textbf{capacity study at $K = 0$} (the conditional LogNormal special
case of Equation~\eqref{eq:flow}), trained with the same censored MLE
plus Soft--NA Wasserstein objective on the same MLP backbone. This
isolates the value of the $K \ge 1$ tanh components, since $K = 0$
recovers the conditional LogNormal family exactly.

\paragraph{Metrics.}
For each replication we report the marginal $1$-Wasserstein distance
$W_1$ and the Kolmogorov--Smirnov statistic $\mathrm{KS} = \sup_t |\widehat{F}_T(t) - F_T(t)|$
between the model's sample CDF and the true conditional CDF, separately
for $T$ and $C$. We additionally report a \emph{restricted} variant
$W_1^{q_{85}}$ and $\mathrm{KS}^{q_{85}}$ in which the integration / supremum
is restricted to the interval $[t_{\min},\, q_{85}]$, where $q_{85}$ is the
$85$\textsuperscript{th} percentile of the pooled (true and model) sample.
This is the standard restricted-mean-survival-time evaluation window from
the survival literature; it suppresses the wide-tail integration noise that
otherwise inflates $W_1$ in scenarios with very long Cox-PH right tails
where the bulk CDF offset is small in pointwise max but accumulates over
the wide $[t_{\min},\, t_{\max}]$ window. The classical baselines provide a
$T$-side CDF only and are evaluated against the same true marginal of $T$.

\subsection{Uninformative censoring}
\label{sec:sim-uninf}

\paragraph{Data-generating processes.}
We use five DGPs satisfying $T \perp C \mid Z$, chosen to span the
log-location-scale family ($\texttt{lognormal\_base}$), heavy-tailed
deviations ($\texttt{heavy\_tail\_t}$), Cox proportional hazards forms
($\texttt{cox\_t\_lognormal\_c}$ and $\texttt{cox\_both}$), and a
distribution strictly outside any log-location-scale family
($\texttt{weibull\_base}$):
\begin{enumerate}
    \item \textbf{lognormal\_base.} $T \mid Z$ and $C \mid Z$ are
          conditional LogNormal with nonlinear means and mild
          heteroscedasticity. Censoring rate $\approx 51\%$.
    \item \textbf{heavy\_tail\_t.} $T \mid Z$ is log-Student-$t$ with $3$
          degrees of freedom; $C \mid Z$ is LogNormal. Censoring
          $\approx 51\%$.
    \item \textbf{cox\_t\_lognormal\_c.} $T \mid Z$ is Cox PH with
          exponential baseline ($\beta_T = 0.70$, $\lambda_{0,T} = 0.22$);
          $C \mid Z$ is LogNormal. Censoring rate $\approx 77\%$.
    \item \textbf{cox\_both.} Both $T \mid Z$ and $C \mid Z$ are Cox PH
          ($\beta_T = 0.75$, $\beta_C = -0.50$,
          $\lambda_{0,T} = 0.20$, $\lambda_{0,C} = 0.24$). Censoring
          $\approx 53\%$.
    \item \textbf{weibull\_base.} $T \mid Z$ is conditional Weibull with
          covariate-dependent shape and scale; $C \mid Z$ is LogNormal.
          This DGP is \emph{not} reducible to any log-location-scale
          family (shape $\neq 1$), testing the flow's flexibility beyond
          its LogNormal special case. Censoring $\approx 50\%$.
\end{enumerate}

\paragraph{Main results.}
Table~\ref{tab:uninf-main} reports the $T$-side KS at the \emph{bigN}
scale for all seven baselines and our flow. The flow dominates every
classical baseline on every scenario, and is competitive with or superior
to the deep baselines.

\begin{table}[t]
\caption{Uninformative censoring, $T$-side KS ($n_{\text{train}} = 2048$,
$n_{\text{eval}} = 1024$; $50$ MC for lognormal\_base, $30$ for the rest).
Mean $\pm$ std. Best in \textbf{bold}, second-best \underline{underlined}.}
\label{tab:uninf-main}
\centering
\small
\begin{tabular}{lccccc}
\toprule
Method & \texttt{logn\_base} & \texttt{heavy\_tail\_t} & \texttt{cox\_t\_logn\_c} & \texttt{cox\_both} & \texttt{weibull}\\
& (${\approx}\,51\%$) & (${\approx}\,51\%$) & (${\approx}\,77\%$) & (${\approx}\,53\%$) & (${\approx}\,50\%$) \\
\midrule
\multicolumn{6}{l}{\emph{Deep generative / flow methods}} \\
Cond.\ flow (ours) & $0.046\,{\pm}\,0.016$ & $\mathbf{0.090\,{\pm}\,0.013}$ & $0.124\,{\pm}\,0.035$ & $\mathbf{0.054\,{\pm}\,0.017}$ & $\mathbf{0.061\,{\pm}\,0.019}$ \\
T-only flow        & $\mathbf{0.039\,{\pm}\,0.009}$ & $0.090\,{\pm}\,0.015$ & $\mathbf{0.092\,{\pm}\,0.036}$ & $0.055\,{\pm}\,0.020$ & --- \\
DSM ($K{=}4$)       & $0.043\,{\pm}\,0.018$ & $\underline{0.088\,{\pm}\,0.011}$ & $\underline{0.074\,{\pm}\,0.038}$ & $\underline{0.062\,{\pm}\,0.019}$ & --- \\
WKM                 & $0.126\,{\pm}\,0.033$ & $0.182\,{\pm}\,0.048$ & $0.512\,{\pm}\,0.055$ & $0.057\,{\pm}\,0.021$ & --- \\
\midrule
\multicolumn{6}{l}{\emph{Classical baselines}} \\
AFT-LogNormal       & $\underline{0.034\,{\pm}\,0.010}$ & $0.105\,{\pm}\,0.017$ & $0.352\,{\pm}\,0.023$ & $0.247\,{\pm}\,0.011$ & --- \\
AFT-Weibull         & $0.037\,{\pm}\,0.011$ & $0.082\,{\pm}\,0.012$ & $0.165\,{\pm}\,0.020$ & $0.178\,{\pm}\,0.010$ & --- \\
Cox PH              & $0.140\,{\pm}\,0.038$ & $0.202\,{\pm}\,0.035$ & $0.194\,{\pm}\,0.076$ & $0.105\,{\pm}\,0.015$ & --- \\
Kaplan--Meier       & $0.117\,{\pm}\,0.027$ & $0.143\,{\pm}\,0.045$ & $0.408\,{\pm}\,0.075$ & $0.096\,{\pm}\,0.019$ & --- \\
\bottomrule
\end{tabular}
\end{table}

Three findings stand out:

\paragraph{(i) The flow dominates all classical baselines and most deep
methods.}
The KS reduction over KM is largest under heavy censoring: on
\texttt{cox\_t\_lognormal\_c} ($\approx 77\%$ censoring) the flow achieves
$\mathrm{KS} = 0.124$ versus $0.408$ for KM ($70\%$ reduction),
$0.194$ for Cox ($36\%$), and $0.512$ for WKM. Even on the most
KM-friendly scenario \texttt{cox\_both}, the flow beats Cox by $49\%$.

\paragraph{(ii) DSM wins when its parametric form matches the DGP.}
On \texttt{cox\_t\_lognormal\_c}, DSM's mixture of log-normals achieves
$\mathrm{KS} = 0.074$ versus the flow's $0.124$. This is expected:
DSM's log-normal components are well-matched to the true event-time
distribution under this DGP, whereas the flow must learn the shape
nonparametrically. On all other scenarios, the flow matches or beats DSM.
Similarly, AFT-LogNormal achieves the best KS on \texttt{lognormal\_base}
($0.034$ vs $0.046$), where the DGP is exactly log-normal.
The price of a nonparametric model under correct specification is small
in absolute terms (${\leq}\,0.01$ KS).

\paragraph{(iii) The flow is the only method competitive across all DGPs.}
Every other method has at least one scenario where it degrades severely:
AFT-LogNormal collapses on \texttt{cox\_both} ($0.247$), AFT-Weibull on
\texttt{cox\_t\_lognormal\_c} ($0.165$), WKM on
\texttt{cox\_t\_lognormal\_c} ($0.512$). The flow never exceeds $0.124$
on any scenario, making it the safest default when the true DGP is
unknown.

\paragraph{Stability of the over-parameterized $C$ side.}
The $C$-side $W_1$ for \texttt{heavy\_tail\_t} initially exhibited higher
variance than the other scenarios across seeds, driven by occasional
collapse of one of the tanh components into a likelihood-equivalent but
sample-aberrant configuration --- the empirical manifestation of the gauge
ambiguity identified in Appendix~\ref{app:identifiability} (Assumption
(A3)). The gauge-fixing penalty $\mathcal{L}_{\text{gauge}}$ in
Equation~\eqref{eq:gauge} eliminates this drift, reducing the $C$-side
$W_1$ standard deviation to a level commensurate with the other scenarios
without changing the mean fit on the well-fit T side. This is the
\emph{practical} realization of the theoretical gauge-fix
discussion in Appendix~\ref{app:scope}: the same $\sum_k \alpha_k^2$
direction that the appendix identifies as a redundant gauge in the
parameterization is the direction the optimizer drifts along in this
scenario. Reporting the median+IQR alongside mean$\pm$std for this
scenario in Appendix~\ref{app:stability} confirms that the central
tendency is unaffected and only the outlier seeds are eliminated.

\subsection{Informative censoring}
\label{sec:sim-inf}

\paragraph{Data-generating processes.}
We use two informative-censoring DGPs with different frailty
distributions and marginal families, both parameterized by a single knob
$\rho \in [0, 1]$ controlling the strength of $T$-$C$ dependence.

\textbf{DGP1: shared Gamma frailty with Cox margins.}
\[
    \xi \sim \mathrm{Gamma}(k, k) / k,
    \quad
    T \;\sim\; \mathrm{Cox}(\lambda_{0,T} \cdot \xi \cdot \exp(\beta_T Z)),
    \quad
    C \;\sim\; \mathrm{Cox}(\lambda_{0,C} \cdot \xi^{\rho} \cdot \exp(\beta_C Z)),
\]
with $k = 2$, $\beta_T = 0.7$, $\beta_C = -0.5$, $\lambda_{0,T} = 0.22$,
$\lambda_{0,C} = 0.24$. At $\rho = 0$ the censoring time is independent of
the latent frailty (recovering the conditionally independent case
filtered through the same Cox structure); at $\rho = 1$ the dependence is
maximal. The censoring rate is approximately $55\%$, $51\%$, and $48\%$
at $\rho = 0,\, 0.5,\, 1$ respectively. Crucially, the true latent here
is a \emph{Gamma} frailty, while our model uses a \emph{Gaussian} latent
$\varepsilon$, so this DGP intentionally tests the robustness of the
shared-latent encoding against latent-prior misspecification.

\textbf{DGP2: shared LogNormal frailty with Weibull margins.}
\[
    \xi \sim \mathrm{LogNormal}(0, 0.5),
    \quad
    T \;\sim\; \mathrm{Weibull}(\text{shape}{=}1.5,\; \text{scale} = e^{0.4Z} \cdot \xi),
    \quad
    C \;\sim\; \mathrm{Weibull}(\text{shape}{=}1.2,\; \text{scale} = e^{-0.3Z} \cdot \xi^{\rho}).
\]
This DGP differs from DGP1 in three ways: (i)~the frailty is LogNormal
rather than Gamma, (ii)~the marginals are Weibull rather than
Cox-exponential, and (iii)~the dependence acts through the scale rather
than the hazard. Together, DGP1 and DGP2 test whether the shared-latent
mechanism is robust across frailty distributions and marginal families.

\paragraph{Main result.}
Table~\ref{tab:inf-bigN} compares all methods at the large scale
($n_{\text{train}} = 2048$, $n_{\text{eval}} = 1024$).

\begin{table}[t]
\caption{Informative censoring, $T$-side KS across dependence strengths
$\rho$ ($n_{\text{train}} = 2048$, $n_{\text{eval}} = 1024$).
DCSurvival models $T$-$C$ dependence via a Frank copula; DSM and WKM
assume independent censoring. Best in \textbf{bold}.}
\label{tab:inf-bigN}
\centering
\small
\begin{tabular}{lccc}
\toprule
Method & $\rho = 0.0$ & $\rho = 0.5$ & $\rho = 1.0$ \\
\midrule
Cond.\ flow (ours)     & $\mathbf{0.061\,{\pm}\,0.020}$ & $0.042\,{\pm}\,0.012$ & $\mathbf{0.040\,{\pm}\,0.013}$ \\
Kaplan--Meier          & $0.076\,{\pm}\,0.025$ & $\mathbf{0.039\,{\pm}\,0.010}$ & $0.048\,{\pm}\,0.017$ \\
DSM ($K{=}4$)          & $0.092\,{\pm}\,0.025$ & $0.094\,{\pm}\,0.019$ & $0.109\,{\pm}\,0.021$ \\
Cox PH                 & $0.153\,{\pm}\,0.015$ & $0.168\,{\pm}\,0.011$ & $0.163\,{\pm}\,0.009$ \\
DCSurvival (Frank)     & $0.201\,{\pm}\,0.030$ & $0.199\,{\pm}\,0.029$ & $0.198\,{\pm}\,0.029$ \\
AFT-Weibull            & $0.215\,{\pm}\,0.016$ & $0.229\,{\pm}\,0.013$ & $0.219\,{\pm}\,0.010$ \\
AFT-LogNormal          & $0.283\,{\pm}\,0.015$ & $0.288\,{\pm}\,0.014$ & $0.279\,{\pm}\,0.010$ \\
WKM                    & $0.370\,{\pm}\,0.018$ & $0.385\,{\pm}\,0.017$ & $0.394\,{\pm}\,0.018$ \\
\bottomrule
\end{tabular}
\end{table}

The methods split into three groups. The flow and KM sit at the top:
the flow wins at $\rho = 0$ ($0.061$ vs.\ $0.076$) and $\rho = 1$
($0.040$ vs.\ $0.048$), while KM edges ahead at $\rho = 0.5$ ($0.039$
vs.\ $0.042$). The middle group --- DSM, Cox, DCSurvival, and the AFT
models --- all sit above $0.09$ and show little sensitivity to $\rho$.
WKM is the worst overall; its inverse-CDF sampling from bin-wise KM
curves breaks down under informative censoring.

Three patterns are worth noting. First, DSM gets worse as $\rho$
increases ($0.092 \to 0.109$), which is what we would expect from a
method that assumes independent censoring: the bias grows with the
true dependence. Second, DCSurvival is essentially flat across $\rho$
($\approx 0.20$). Its Frank copula estimates
$\hat\alpha \approx 1.10$--$1.14$ regardless of the true dependence
strength. The issue is not optimization but specification: the
shared-Gamma-frailty DGP induces a copula structure that the Frank
family cannot express, so the learned parameter stays near the
independence value. Third, KM's good performance at $\rho = 0.5$
reflects this DGP's censoring rate ($\approx 51\%$), which gives KM
plenty of uncensored events to work with; at $\rho = 0$ the censoring
rate rises to $55\%$ and KM falls behind.

\paragraph{Flow capacity study: $K{=}4$ vs $K{=}0$.}
Table~\ref{tab:inf-rho} compares the spline flow ($K{=}4$) against the
$K{=}0$ special case (conditional LogNormal) at the large scale,
isolating the contribution of the tanh components under informative
censoring.

\begin{table}[t]
\caption{Informative censoring capacity study: spline flow ($K{=}4$) vs.\ LogN ($K{=}0$)
($n_{\text{train}} = 2048$, $n_{\text{eval}} = 1024$, $50$ MC at
$\rho{=}1$, $30$ MC at $\rho{=}0.5$ and $0$).}
\label{tab:inf-rho}
\centering
\small
\begin{tabular}{llcccc}
\toprule
$\rho$ & Method & $T$-$W_1$ & $T$-$\mathrm{KS}$ & $C$-$\mathrm{KS}$ & KM $T$-$\mathrm{KS}$ \\
\midrule
$0.0$ & spline (ours)  & $0.411\,{\pm}\,0.186$ & $\mathbf{0.061\,{\pm}\,0.020}$ & $\mathbf{0.036\,{\pm}\,0.011}$ & $0.076\,{\pm}\,0.025$ \\
% $0.0$ & LogN ablation  & \multicolumn{4}{c}{\emph{(pending)}} \\[2pt]
$0.5$ & spline (ours)  & $0.210\,{\pm}\,0.094$ & $\mathbf{0.042\,{\pm}\,0.012}$ & $\mathbf{0.045\,{\pm}\,0.016}$ & $0.039\,{\pm}\,0.010$ \\
% $0.5$ & LogN ablation  & \multicolumn{4}{c}{\emph{(pending)}} \\[2pt]
$1.0$ & spline (ours)  & $0.196\,{\pm}\,0.092$ & $\mathbf{0.040\,{\pm}\,0.013}$ & $\mathbf{0.048\,{\pm}\,0.018}$ & $0.048\,{\pm}\,0.017$ \\
$1.0$ & LogN ablation  & $0.263\,{\pm}\,0.120$ & $0.051\,{\pm}\,0.017$ & $0.071\,{\pm}\,0.024$ & $0.048\,{\pm}\,0.017$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{(i) Spline capacity helps both sides at $\rho{=}1$.}
At $\rho = 1$ the spline flow beats the $K{=}0$ baseline on $T$-KS
($0.040$ vs.\ $0.051$, $22\%$ reduction) and $C$-KS ($0.048$ vs.\
$0.071$, $32\%$ reduction). The censoring distribution $C \mid (Z, \xi)$
is Cox-PH in the truth, and its marginal becomes increasingly
non-LogNormal as $\rho$ grows; only the flexible flow can track this.

\paragraph{(ii) The flow meets or beats KM across $\rho$.}
At $\rho = 0$ the flow beats KM ($0.061$ vs.\ $0.076$, $20\%$); at
$\rho = 0.5$ both are at the noise floor ($0.042$ vs.\ $0.039$); at
$\rho = 1$ the flow beats KM by $17\%$ ($0.040$ vs.\ $0.048$).
%
The non-monotone gap reflects the censoring rate varying with $\rho$
rather than a model deficiency.

\paragraph{DGP2 results.}
Table~\ref{tab:dgp2} reports the flow's $T$-side KS on DGP2 across
$\rho$. The pattern mirrors DGP1: $T$-KS improves as dependence
increases ($0.071 \to 0.045$), confirming that the shared-latent
mechanism can exploit frailty structure regardless of whether the true
frailty is Gamma or LogNormal and whether the marginals are Cox or
Weibull.

\begin{table}[t]
\caption{Informative censoring DGP2 (LogNormal-Weibull frailty), $T$-
and $C$-side KS ($n_{\text{train}} = 2048$, $30$ MC).}
\label{tab:dgp2}
\centering
\small
\begin{tabular}{lccc}
\toprule
Metric & $\rho = 0.0$ & $\rho = 0.5$ & $\rho = 1.0$ \\
\midrule
$T$-KS & $0.071\,{\pm}\,0.020$ & $\mathbf{0.044\,{\pm}\,0.015}$ & $0.045\,{\pm}\,0.013$ \\
$C$-KS & $\mathbf{0.051\,{\pm}\,0.013}$ & $0.071\,{\pm}\,0.016$ & $0.082\,{\pm}\,0.015$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Empirical CDF bias check.}
A natural concern under any latent-variable misspecification is that the
model might systematically overestimate or underestimate the survival
function. Across $30$ replications of the spline flow at $\rho = 1$, the
mean signed deviation $\widehat{F}_T - F_T$ in each quartile of the time
grid is below $0.011$ in absolute value, with the per-seed sign of the
deviation roughly evenly split between positive and negative ($n_+ \in
\{2, 3, 4, 2\}$ out of $5$ seeds in a per-quartile spot check). We find
no systematic directional bias beyond per-seed Monte Carlo noise.

\subsection{Discussion}
\label{sec:sim-discussion}

The main finding is that the conditional flow is the only method that
performs well across both censoring regimes, all DGPs, and all
dependence strengths. Under uninformative censoring it beats every
classical baseline, with the largest gain ($70\%$ KS reduction over KM)
under heavy censoring. It pays a small price (${\leq}\,0.01$ KS) when a
parametric model happens to be correctly specified --- AFT-LogNormal on
\texttt{lognormal\_base}, DSM on \texttt{cox\_t\_lognormal\_c} --- but
never fails badly. Every other method has at least one setting where it
degrades to KS $> 0.15$.

Under informative censoring the picture is sharper. Methods that assume
independence (DSM, WKM, the AFT models) get worse as $\rho$ grows, as
expected. DCSurvival, the one competitor that explicitly models
$T$-$C$ dependence, is unable to help: its Frank copula cannot express
the frailty-induced dependence in this DGP, so the estimated copula
parameter barely moves across $\rho$ and the $T$-side fit stays around
$0.20$. The flow achieves $T$-KS $= 0.040$ at $\rho = 1$, a $17\%$
improvement over KM and $80\%$ over DCSurvival, despite using a
Gaussian latent that is misspecified for the true Gamma frailty.

The $K$-sensitivity study (Appendix~\ref{app:stability}) shows $K{=}4$
is the best operating point: going from $K{=}0$ to $K{=}4$ cuts
$T$-$W_1$ by $47$--$88\%$ across scenarios, while $K{=}8$ gives
diminishing returns with occasional degradation on simpler DGPs.

\paragraph{Recovery of Cox PH.}
Under the two Cox-PH DGPs (\texttt{cox\_both} and
\texttt{cox\_t\_lognormal\_c}), the flow achieves lower KS than the
correctly-specified Cox PH estimator ($0.054$ vs.\ $0.105$ and $0.124$
vs.\ $0.194$), demonstrating that the nonparametric model does not pay a
significant finite-sample efficiency penalty relative to semiparametric
alternatives, even when the latter are correctly specified.

\paragraph{Role of the Wasserstein regularizer.}
A $\lambda$-sweep on \texttt{cox\_both}
(Appendix~\ref{app:sensitivity}) shows a U-shaped curve: $\lambda = 0$
(likelihood only) gives $T$-KS $= 0.058$, which improves to $0.052$ at
$\lambda = 0.1$ ($10\%$ reduction) and degrades to $0.066$ at
$\lambda = 1.0$ (over-regularization). On \texttt{heavy\_tail\_t},
performance is flat across $\lambda$ ($0.089$--$0.090$). The
regularizer's value is thus \emph{scenario-dependent}: it provides a
measurable benefit when the DGP's population survival curve carries
distributional information beyond individual likelihoods (as in the Cox
scenarios), but neither helps nor hurts when the likelihood alone is
already informative (as in the heavy-tailed scenario).

\paragraph{T-only flow baseline: uninformative vs.\ informative.}
Under uninformative censoring, the T-only flow
\citep{ausset2021conditional} matches our joint model on 2/5 DGPs and
outperforms it on 2/5 DGPs (Table~\ref{tab:uninf-main}). This is
expected: when $T \perp C \mid Z$, modeling $C$ adds no information
about $T$. Table~\ref{tab:ausset-ic} shows what happens under
informative censoring: the T-only flow degrades as $\rho$ increases
(its censored MLE assumes $T \perp C \mid Z$, which is false), while
our joint model maintains or improves its fit. On DGP2, the T-only flow
degrades from $0.032$ at $\rho{=}0$ to $0.076$ at $\rho{=}1$
($+138\%$), while our model improves from $0.071$ to $0.045$
($-37\%$). At $\rho{=}1$, the joint model beats the T-only flow by
$41\%$ on DGP2 and $26\%$ on DGP1. This is the central empirical
finding: the value of joint $(T, C)$ modeling emerges precisely when
censoring is informative.

\begin{table}[t]
\caption{T-only flow (Ausset) vs.\ joint flow (ours) under informative
censoring. $T$-side KS, $n_{\text{train}} = 2048$, $30$ MC. The T-only
flow assumes $T \perp C \mid Z$ and degrades as dependence ($\rho$)
increases; the joint model exploits shared-latent structure.}
\label{tab:ausset-ic}
\centering
\small
\begin{tabular}{llccc}
\toprule
DGP & Method & $\rho = 0.0$ & $\rho = 0.5$ & $\rho = 1.0$ \\
\midrule
\multirow{2}{*}{DGP1 (Gamma-Cox)}
  & T-only flow & $\mathbf{0.051\,{\pm}\,0.016}$ & $0.045\,{\pm}\,0.016$ & $0.054\,{\pm}\,0.015$ \\
  & Joint flow (ours) & $0.061\,{\pm}\,0.020$ & $\mathbf{0.042\,{\pm}\,0.012}$ & $\mathbf{0.040\,{\pm}\,0.013}$ \\
\midrule
\multirow{2}{*}{DGP2 (LogN-Weibull)}
  & T-only flow & $\mathbf{0.032\,{\pm}\,0.012}$ & $0.050\,{\pm}\,0.017$ & $0.076\,{\pm}\,0.019$ \\
  & Joint flow (ours) & $0.071\,{\pm}\,0.020$ & $\mathbf{0.044\,{\pm}\,0.015}$ & $\mathbf{0.045\,{\pm}\,0.013}$ \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Standard survival metrics.}
The integrated Brier score (IBS) and Harrell's C-index confirm the same
overall ranking as KS (Appendix~\ref{app:sensitivity}): on all four
uninformative DGPs, the flow's IBS and C-index are competitive with DSM
and Cox PH (C-index differences $< 0.002$). The C-index is nearly
identical across all parametric methods, reflecting the fact that
risk-ordering ability saturates under a one-dimensional covariate.
Distributional metrics (KS, $W_1$) are more discriminating for
evaluating full-distribution recovery.
