\section{Discussion}
\label{sec:discussion}

We have presented a conditional normalizing flow for jointly modeling
event and censoring times under right censoring, augmented with a
Soft--Nelson--Aalen Wasserstein regularizer and extended to informative
censoring via a shared-latent variable. The approach achieves three
goals simultaneously: (i)~closed-form density and survival function for
exact censored MLE, (ii)~differentiable sampling for end-to-end
distributional regularization, and (iii)~identifiability of the marginal
event-time distribution under dependent censoring.

\paragraph{Where the method helps most.}
The primary value of joint $(T, C)$ modeling emerges under informative
censoring, where methods assuming independence (DSM, WKM, AFT) degrade
as dependence increases. Under uninformative censoring, a simpler T-only
flow achieves comparable $T$-side fit, consistent with the theoretical
expectation that modeling $C$ adds no information about $T$ when they
are conditionally independent. The Wasserstein regularizer provides a
scenario-dependent benefit (up to $10\%$ KS improvement on Cox-PH DGPs)
but is not universally necessary.

\paragraph{Limitations.}
Several limitations should be noted. First, the simulation study uses
one-dimensional covariates; while Rotterdam ($d = 7$) demonstrates
feasibility at moderate dimensionality, scaling to high-dimensional
covariates ($d \gg 10$) remains untested. Second, the identifiability
proof relies on tail-asymptotic arguments and the gauge-fixing
assumption (A3); finite-sample identifiability guarantees would
strengthen the theoretical contribution. Third, training is CPU-based
and full-batch; GPU acceleration and mini-batch training would be
needed for large-scale applications. Fourth, we do not address competing
risks or recurrent events, which require extensions beyond the single
$(T, C)$ framework.

\paragraph{Future work.}
Natural extensions include replacing the tanh basis with rational-quadratic
spline (RQS) coupling layers for improved tail flexibility, extending to
the competing-risks setting with multiple event types, and developing
conformal prediction intervals from the flow's generative samples.
